---
title: "FFW Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation:
    storyboard: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(devtools)
library(WISKIr)
library(ggplot2)
library(plotly)
library(plyr)
library(knitr)
library(kableExtra)
library(flexdashboard)
library(shiny)
#setting rotating date from today's date
dt1 = as.character(Sys.Date() - 15)
# create some data to make plots
#Cold Creek
COLDF<-getWISKIvalues(timeSeries= "3394042", startDate=dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
COLDP<-getWISKIvalues(timeSeries= "3536042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(COLDP)<-c("Date", "Precipitation", "QC")
colnames(COLDF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
COLDT<-na.omit(COLDF)
#Turning the date into a useable format
COLDate<-as.POSIXct(COLDT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
COLDateP<-as.POSIXct(COLDP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
COLDFin<-cbind(COLDT,COLDate)
COLDPFin<-cbind(COLDP,COLDateP)
colnames(COLDFin)<- c("DateO","Discharge","QC","Date")
colnames(COLDPFin)<-c("DateO","Precipitation","QC","Date")

#Mayhew Creek
MayF<-getWISKIvalues(timeSeries= "18125042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
MayP<-getWISKIvalues(timeSeries= "87433042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#Changing the column names
colnames(MayF)<-c("Date", "Discharge","QC")
colnames(MayP)<-c("Date", "Precipitation", "QC")
#Omit the na's
MayFF<-na.omit(MayF)
#Turning the date into a useable format
MayDate<-as.POSIXct(MayFF$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
MayDateP<-as.POSIXct(MayP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
MayFin<-cbind(MayFF,MayDate)
MayPFin<-cbind(MayP,MayDateP)
colnames(MayFin)<- c("DateO","Discharge","QC","Date")
colnames(MayPFin)<-c("DateO","Precipitation","QC","Date")

# Trout Creek

TroutF<-getWISKIvalues(timeSeries= "18208042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
TroutP<-getWISKIvalues(timeSeries= "4508042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(TroutP)<-c("Date", "Precipitation", "QC")
colnames(TroutF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
TroutT<-na.omit(TroutF)
#Turning the date into a useable format
TroutDateF<-as.POSIXct(TroutT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
TroutDateP<-as.POSIXct(TroutP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
TroutFin<-cbind(TroutT,TroutDateF)
TroutPFin<-cbind(TroutP,TroutDateP)
colnames(TroutFin)<- c("DateO","Discharge","QC","Date")
colnames(TroutPFin)<-c("DateO","Precipitation","QC","Date")

#Hoards Creek

HOARDF<-getWISKIvalues(timeSeries= "18129042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
HOARDP<-getWISKIvalues(timeSeries= "3542042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(HOARDP)<-c("Date", "Precipitation", "QC")
colnames(HOARDF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
HOARDT<-na.omit(HOARDF)
#Turning the date into a useable format
HOARDDateF<-as.POSIXct(HOARDT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
HOARDDateP<-as.POSIXct(HOARDP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
HOARDFin<-cbind(HOARDT,HOARDDateF)
HOARDPFin<-cbind(HOARDP,HOARDDateP)
colnames(HOARDFin)<- c("DateO","Discharge","QC","Date")
colnames(HOARDPFin)<-c("DateO","Precipitation","QC","Date")

#Salt Creek

SALTF<-getWISKIvalues(timeSeries= "18126042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
SALTP<-getWISKIvalues(timeSeries= "3540042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(SALTP)<-c("Date", "Precipitation", "QC")
colnames(SALTF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
SALTT<-na.omit(SALTF)
#Turning the date into a useable format
SALTDateF<-as.POSIXct(SALTT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
SALTDateP<-as.POSIXct(SALTP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
SALTFin<-cbind(SALTT,SALTDateF)
SALTPFin<-cbind(SALTP,SALTDateP)
colnames(SALTFin)<- c("DateO","Discharge","QC","Date")
colnames(SALTPFin)<-c("DateO","Precipitation","QC","Date")

#Rawdon Creek

RawF<-getWISKIvalues(timeSeries= "18123042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
RawP<-getWISKIvalues(timeSeries= "3539042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(RawP)<-c("Date", "Precipitation", "QC")
colnames(RawF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
RawT<-na.omit(RawF)
#Turning the date into a useable format
RawDateF<-as.POSIXct(RawT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
RawDateP<-as.POSIXct(RawP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
RawFin<-cbind(RawT,RawDateF)
RawPFin<-cbind(RawP,RawDateP)
colnames(RawFin)<- c("DateO","Discharge","QC","Date")
colnames(RawPFin)<-c("DateO","Precipitation","QC","Date")

#Proctor (Butler) Creek

PROCF<-getWISKIvalues(timeSeries= "18124042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
PROCP<-getWISKIvalues(timeSeries= "3538042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(PROCP)<-c("Date", "Precipitation", "QC")
colnames(PROCF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
PROCT<-na.omit(PROCF)
#Turning the date into a useable format
PROCDateF<-as.POSIXct(PROCT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
PROCDateP<-as.POSIXct(PROCP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
PROCFin<-cbind(PROCT,PROCDateF)
PROCPFin<-cbind(PROCP,PROCDateP)
colnames(PROCFin)<- c("DateO","Discharge","QC","Date")
colnames(PROCPFin)<-c("DateO","Precipitation","QC","Date")

#Shelter Valley Creek

SHELF<-getWISKIvalues(timeSeries= "18119042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
SHELP<-getWISKIvalues(timeSeries= "3541042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(SHELP)<-c("Date", "Precipitation", "QC")
colnames(SHELF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
SHELT<-na.omit(SHELF)
#Turning the date into a useable format
SHELDateF<-as.POSIXct(SHELT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
SHELDateP<-as.POSIXct(SHELP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
SHELFin<-cbind(SHELT,SHELDateF)
SHELPFin<-cbind(SHELP,SHELDateP)
colnames(SHELFin)<- c("DateO","Discharge","QC","Date")
colnames(SHELPFin)<-c("DateO","Precipitation","QC","Date")

#Burnley (Mill) Creek

BURNF<-getWISKIvalues(timeSeries= "18122042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
BURNP<-getWISKIvalues(timeSeries= "3535042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#changing column names
colnames(BURNP)<-c("Date", "Precipitation", "QC")
colnames(BURNF)<-c("Date", "Flow","QC")
#Merging the Precip and Flow dataframes
BURNT<-na.omit(BURNF)
#Turning the date into a useable format
BURNDateF<-as.POSIXct(BURNT$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
BURNDateP<-as.POSIXct(BURNP$Date,format="%yyyy%mm%dd")
#merging the new date/time and the dataframe
BURNFin<-cbind(BURNT,BURNDateF)
BURNPFin<-cbind(BURNP,BURNDateP)
colnames(BURNFin)<- c("DateO","Discharge","QC","Date")
colnames(BURNPFin)<-c("DateO","Precipitation","QC","Date")

#Crowe River Discharge

#CroweF<-getWISKIvalues(timeSeries= "12256042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#Changing the column names
#colnames(CroweF)<-c("Date", "Discharge","QC")
#Omit the na's
#CroweFF<-na.omit(CroweF)
#Turning the date into a useable format
#CroweDate<-as.POSIXct(CroweFF$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
#merging the new date/time and the dataframe
#CroweFin<-cbind(CroweFF,CroweDate)
#colnames(CroweFin)<- c("DateO","Discharge","QC","Date")

##Trent River Sites
#Trent River Upper Glen Ross

UGRF<-getWISKIvalues(timeSeries= "3396042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#Changing the column names
colnames(UGRF)<-c("Date", "Water Level","QC")
#Omit the na's
UGRFF<-na.omit(UGRF)
#Turning the date into a useable format
UGRDate<-as.POSIXct(UGRFF$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
#merging the new date/time and the dataframe
UGRin<-cbind(UGRFF,UGRDate)
colnames(UGRin)<- c("DateO","WaterLevel","QC","Date")

#Lower Glen Ross
LGRF<-getWISKIvalues(timeSeries= "3397042", startDate= dt1, timezone="GMT-5", site.url="http://waterdata.quinteconservation.ca/")
#Changing the column names
colnames(LGRF)<-c("Date", "Water Level (m)","QC")
#Omit the na's
LGRFF<-na.omit(LGRF)
#Turning the date into a useable format
LGRDate<-as.POSIXct(LGRFF$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
#merging the new date/time and the dataframe
LGRin<-cbind(LGRFF,LGRDate)
colnames(LGRin)<- c("DateO","WaterLevel","QC","Date")

#Percy Boom Removed


#Lake Ontario
LakeO<-getWISKIvalues(timeSeries= "946325042", startDate= dt1, timezone="GMT-5", site.url="https://www.swmc.mnr.gov.on.ca/")
colnames(LakeO)<-c("Date", "WaterLevel","QC")
#Merging the Precip and Flow dataframes
LakeOnt<-na.omit(LakeO)
#Turning the date into a useable format
LakeOntF<-as.POSIXct(LakeOnt$Date,format="%yyyy%mm%dd %HH:%MM:%SS:%ssss")
#merging the new date/time and the dataframe
LakeOntFin<-cbind(LakeO,LakeOntF)
colnames(LakeOntFin)<- c("DateO","WaterLevel","QC","Date")



Cold_Creek<-tail(COLDFin$Discharge,1)
Mayhew_Creek<-tail(MayFin$Discharge,1)
Rawdon_Creek<-tail(RawFin$Discharge,1)
Proctor_Creek<-tail(PROCFin$Discharge,1)
Hoards_Creek<-tail(HOARDFin$Discharge,1)
Salt_Creek<-tail(SALTFin$Discharge,1)
Shelter_Valley_Creek<-tail(SHELFin$Discharge,1)
Trout_Creek<-tail(TroutFin$Discharge,1)
Burnley_Creek<-tail(BURNFin$Discharge,1)
#Crowe_River<-tail(CroweFin$Discharge,1)


ColdRecentD<-tail(COLDFin$Date,1)
MayhewRecentD<-tail(MayFin$Date,1)
RawdonRecentD<-tail(RawFin$Date,1)
ProctorRecentD<-tail(PROCFin$Date,1)
HoardsRecentD<-tail(HOARDFin$Date,1)
SaltRecentD<-tail(SALTFin$Date,1)
ShelterRecentD<-tail(SHELFin$Date,1)
TroutRecentD<-tail(TroutFin$Date,1)
BurnleyRecentD<-tail(BURNFin$Date,1)
#CroweRecentD<-tail(CroweFin$Date,1)



Tribs<- rbind(Cold_Creek,Mayhew_Creek,Rawdon_Creek,Proctor_Creek,Hoards_Creek,Salt_Creek,Shelter_Valley_Creek,Trout_Creek,Burnley_Creek)
Dates<-c(ColdRecentD,MayhewRecentD,RawdonRecentD,ProctorRecentD,HoardsRecentD,SaltRecentD,ShelterRecentD,TroutRecentD,BurnleyRecentD)
Date1<- as.character.Date(Dates)

RecentFlow<-cbind(Date1,Tribs)
colnames(RecentFlow)<- c("Date/Time", "Discharge (cumec)")
rownames(RecentFlow)<-c("Cold Creek","Mayhew Creek", "Rawdon Creek", "Proctor Creek", "Hoards Creek", "Salt Creek", "Shelter Valley", "Trout Creek", "Burnley Creek")




UpperGlen<-tail(UGRin$WaterLevel,1)
LowerGlen<-tail(LGRin$WaterLevel,1)
LakeONT<- tail(LakeOntFin$WaterLevel,1)


UpperGlenD<-tail(UGRin$Date,1)
LowerGlenD<-tail(LGRin$Date,1)
LakeONTD<- tail(LakeOntFin$Date,1)
River<- rbind(UpperGlen,LowerGlen,LakeONT)
DatesR<-c(UpperGlenD,LowerGlenD,LakeONTD)
Date2<- as.character.Date(DatesR)

RecentLevel<-cbind(Date2,River)
colnames(RecentLevel)<- c("Date/Time", "Water Level (masL)")
rownames(RecentLevel)<-c("Upper Glen Ross", "Lower Glen Ross", "Lake Ontario")


TRCLevels<-read.csv("Trent River Concern Levels.csv")
colnames(TRCLevels)<- c("","Rice Lake", "Percy Boom", "Upper Glen Ross", "Lower Glen Ross")


```

# Summary

## Row

### Concern Levels

```{r}
TRCLevels%>% kable(booktabs=TRUE)%>% kable_styling()

```

### Current Observed Water Level {.no-mobile}

```{r}
#RecentLevel%>% kable(booktabs=TRUE)%>% kable_styling()%>%footnote(number=c("masl= metres above sea level"))

createTable <- function(df, tableHeight = 50){
  
  # Create the value parameters
  # Headers
  nms <- lapply(names(df), function(x){
    return(paste0("<b>", x, "</b>"))    
  })
  
  nms <- append(nms, "<b>Rows</b>", after = 0)
  headerValues <- lapply(nms, function(x){return(list(x))})
  
  # Cell values
  names(df) <- NULL
  cellValues <- apply(df, 2, function(x){return(list(x))})
  cellValues <- lapply(cellValues, function(x){return(unlist(x))})
  
  cellValues <- append(cellValues, list(rownames(df)), after = 0)
  
  # Create the list to pass to plot_ly()
  header <- list(
    values = headerValues, 
    
    # Formatting 
    line = list(color = '#DFE8F3'),
    align = c('left', rep('center', ncol(df))),
    font = list(color = '#ffffff', size = 16),
    fill = list(color = '#999999')
  )
  
  cells <- list(
    values = cellValues,
    
    # Formatting
    line = list(color = '#DFE8F3'),
    align = c('left', rep('center', ncol(df))),
    font = list(color = c('#262626'), size = 14),
    fill = list(color = c("FFFFFF", rep("FFFFFF", ncol(df)))),
    height = tableHeight
  )
  
  # Create table in plotly
  p <- plot_ly(
    type = "table",
    header = header,
    cells = cells,
    width = 800, 
    height = 1000) %>% 
    
    layout(xaxis = list(zeroline = F, showgrid = F, showticklabels = F),
           yaxis = list(zeroline = F, showgrid = F, showticklabels = F))
  
  return(p)
}

RecentLEV<-as.data.frame(RecentLevel)
p <- createTable(RecentLEV)
p
##d9d9d9
```

### Current Observed Water Level {.mobile}

```{r}
RecentLevel%>% kable(booktabs=TRUE)%>% kable_styling()
```

## Row

### Current Observed Flow {.no-mobile}

```{r}
#RecentFlow%>% kable(booktabs=TRUE)%>% kable_styling()%>%footnote(number=c("cms= cubic metres per second"))
createTable <- function(df, tableHeight = 30){
  
  # Create the value parameters
  # Headers
  nms <- lapply(names(df), function(x){
    return(paste0("<b>", x, "</b>"))    
  })
  
  nms <- append(nms, "<b>Rows</b>", after = 0)
  headerValues <- lapply(nms, function(x){return(list(x))})
  
  # Cell values
  names(df) <- NULL
  cellValues <- apply(df, 2, function(x){return(list(x))})
  cellValues <- lapply(cellValues, function(x){return(unlist(x))})
  
  cellValues <- append(cellValues, list(rownames(df)), after = 0)
  
  # Create the list to pass to plot_ly()
  header <- list(
    values = headerValues, 
    
    # Formatting 
    line = list(color = '#DFE8F3'),
    align = c('left', rep('center', ncol(df))),
    font = list(color = '#ffffff', size = 16),
    fill = list(color = '#999999')
  )
  
  cells <- list(
    values = cellValues,
    
    # Formatting
    line = list(color = '#DFE8F3'),
    align = c('left', rep('center', ncol(df))),
    font = list(color = c('#262626'), size = 14),
    fill = list(color = c("FFFFFF", rep("FFFFFF", ncol(df)))),
    height = tableHeight
  )
  
  # Create table in plotly
  p <- plot_ly(
    type = "table",
    header = header,
    cells = cells,
    width = 800, 
    height = 1000) %>% 
    
    layout(xaxis = list(zeroline = F, showgrid = F, showticklabels = F),
           yaxis = list(zeroline = F, showgrid = F, showticklabels = F))
  
  return(p)
}

RecentFLO<-as.data.frame(RecentFlow)
p <- createTable(RecentFLO)
p
```

### Current Observed Flow {.mobile}

```{r}
RecentFlow%>% kable(booktabs=TRUE)%>% kable_styling()
```

### 

Add 74.2 to Lake Ontario to obtain current water level

masL- metres above sea level

cumec- cubic metres per second

Data shown on this dashboard is updated two times a day.

Provisional data: The data provided on this page is in its raw form and has not been checked for errors/omissions. Anyone using this data is cautioned to carefully consider the provisional nature of this information and should not use it for making decisions that concern personal or public safety. Lower Trent Conservation and its employees accept no responsibility for any loss, damage, injury, or loss in value to any person, property, service or otherwise, resulting from its use.

# Trout

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
TCD<-ggplot(TroutFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=7, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=3.5, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.3), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(3.7), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(TCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
TCPG<-ggplot(TroutPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(TCPG)
```

# Burnley

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
BCD<-ggplot(BURNFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=14, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=7, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(14.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.5), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(BCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
BCPG<-ggplot(BURNPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(BCPG)
```

# Salt

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
SCD<-ggplot(SALTFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=14, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=7, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(14.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.5), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(SCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
SCPG<-ggplot(SALTPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(SCPG)
```

# Hoards

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
HCD<-ggplot(HOARDFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=17, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=8.5, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(17.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(8.7), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(HCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
HCPG<-ggplot(HOARDPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(HCPG)
```

# Rawdon

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
RCD<-ggplot(RawFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=12, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=6, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin = ), y = c(12.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(6.5), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(RCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
RCPG<-ggplot(RawPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(RCPG)
```

# Cold

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
CCOD<-ggplot(COLDFin, aes(x=Date, y=Discharge))+ylab("Discharge (cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=24, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=12, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin = ), y = c(24.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1,origin=), y = c(12.5), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")

ggplotly(CCOD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
CCOP<-ggplot(COLDPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(CCOP)

```

# Mayhew

## Row {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
MayD<-ggplot(MayFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+geom_line(color = "blue")+ geom_hline(yintercept=7, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=3.5, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.3), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(3.8), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")

ggplotly(MayD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
MayP<-ggplot(MayPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(MayP)

```

# Butler

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
PCD<-ggplot(PROCFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=6.8, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=3.4, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.1), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(3.6), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(PCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
PCPG<-ggplot(PROCPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(PCPG)
```

# ShelterValley

## Column {data-height="800"}

### Discharge (Cubic Metres per Second)

```{r}
SVCD<-ggplot(SHELFin, aes(x=Date, y=Discharge))+ylab("Discharge(cumec)")+ geom_line(color = "blue")+ geom_hline(yintercept=14, linetype="dashed", color="red", size=1)+ geom_hline(yintercept=7, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin = ), y = c(14.5), label = c("2 Year Flow") , color="Black", size=3 , angle=1800, fontface="bold")+ annotate("text", x=as.POSIXct(dt1, origin =), y = c(7.5), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(SVCD)
```

## Column {data-height="800"}

### Total Precipitation (mm)

```{r}
SVPG<-ggplot(SHELPFin, aes(x=Date, y=Precipitation))+labs(y="Total Daily Precipitation (mm)")+geom_bar(stat="identity", colour="black")
ggplotly(SVPG)
```

# Upper Glen Ross (TR.)

## Row

### Water Level (m)

```{r}
UGRD<-ggplot(UGRin, aes(x=Date, y=WaterLevel))+labs(y="Water Level (m)")+ geom_line(color = "blue")
ggplotly(UGRD)
```

# Lower Glen Ross (TR.)

## Row

### Water Level (m)

```{r}
LGRD<-ggplot(LGRin, aes(x=Date, y=WaterLevel))+labs(y="Water Level (m)")+ geom_line(color = "blue")+ geom_hline(yintercept=111.65, linetype="dashed", color="red", size=1)+ annotate("text", x=as.POSIXct(dt1, origin = ), y = c(111.66), label = c("Concern Level") , color="Black", size=3 , angle=1800, fontface="bold")
ggplotly(LGRD)
```

# Lake Ontario

```{r}
Lake<-ggplot(LakeOntFin, aes(x=Date, y=WaterLevel))+labs(y="Water Level (m)")+ geom_line(color = "blue")
ggplotly(Lake)

```

# Site Map

```{r}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addMarkers(lng=-77.61250, lat=44.108889, popup="Mayhew Creek (02HK011)") %>%
  addMarkers(lng=-78.001111, lat=43.991667, popup="Shelter Valley Creek (02HD010)")%>%
  addMarkers(lng=-77.744444, lat=44.059722, popup="Proctor (Butler) Creek (02HD018)")%>%
  addMarkers(lng=-77.830833, lat=44.301667, popup="Trout Creek (02HK016)")%>%
  addMarkers(lng=-77.910833, lat=44.196667, popup="Burnley (Mill) Creek (02HK009)")%>%
  addMarkers(lng=-77.786944, lat=44.134722, popup="Cold Creek (02HK007)")%>%
  addMarkers(lng=-77.818889, lat=44.199444, popup="Salt Creek (02HK015)")%>%
  addMarkers(lng=-77.477222, lat=44.338333, popup="Rawdon Creek (02HK008)")%>%
  addMarkers(lng=-77.628333, lat=44.331667, popup="Squires (Hoards) Creek (02HK017)")%>%
  addMarkers(lng=-78.183066, lat=44.144521, popup="Rice Lake at Harwood")%>%
  addMarkers(lng=-77.782189, lat=44.235639, popup="Percy Boom")%>%
  addMarkers(lng=-77.598785, lat=44.265537, popup="Upper Glen Ross")%>%
  addMarkers(lng=-77.595407, lat=44.266704, popup="Lower Glen Ross")%>%
  addMarkers(lng=-77.787202, lat=44.377000, popup="Healey Falls")%>%
  addMarkers(lng=-78.167917, lat=43.952278, popup= "Cobourg (#13590)")

```
